Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-06-06 code/rmarkdown/article.Rmd
+ use new version of rapr + fix bug where numreps in bayescan is ignored + use correct clumpp parameters for data

### Adaptive and neutral genetic data
To investigate the effectiveness of our supposed surrogates for adaptive and neutral genetic variation, we first needed to identify which of the sampled loci--if any--were adaptive. We used two outlier detection methods to achieve this [an individual- and a population-level method as recommended by @r495]. We omitted the species \textit{`r gsub('_', ' ' , missing.species, fixed=TRUE)`} from all subsequent analyses because it was not compatible with one of the outlier detection methods (see below). The basic premise underpinning such methods is that neutral loci are expected to exhibit a specific level of variation among populations, and loci that deviate from this expectation should be under selection [reviewed in @r480]. The advantage of these methods--in contrast with environmental association analyses [@r489]--is that they do not use environmental data to identify loci under selection, which would have biased our analysis. Loci identified as outliers in both analyses were treated as adaptive and the rest were treated as neutral. To avoid false-positives, we omitted loci from both outlier detection methods where the global frequency of the minor allele was $> 0.1$ and assumed they were neutral.

First, we used multinominal-Dirichlet models implemented in \texttt{BayeScan} [version 2.1; @r456] to identify loci under selection. We adopted a similar methodology to Bothwell _et al._ [-@r455] and applied it to each of the species in the data set. Following this methodology, for each species, we first grouped individuals into genetic lineages to avoid falsely classifying loci as adaptive. We used the number of genetic lineages identified in a previous analysis of the data set [@r478]. Since \textit{`r gsub('_', ' ' , missing.species, fixed=TRUE)`} was found to only contain a single lineage/population, it was not compatible with these models. For each species, we used \texttt{Structure} [version 2.3.4; using same parameters as @r478 per run with `r structure.params.LST[[MODE]]$numruns` runs per species] and \texttt{ClumPP} [version 1.1.2; @r459] to group individuals into populations. We then ran $\texttt{Bayescan}$ for each species using these groupings [1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; @r456].  Additionally, we omitted individuals from this analysis when their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate [$q \leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

Second, we used PCAs to identify outlier loci [using methods implemented in the \texttt{pcadapt R} package; version 3.0; @r487; @r496]. To enable comparisons between the two outlier detection analyses, we used the same individuals in this analysis as used in the \texttt{BayeScan} analysis. For each of the 26 species, we first imputed missing data to permit further analysis. Specifically, the missing value for a given locus for a given individual was replaced with the average frequency of that locus among all conspecifics. Next, we ran a PCA and extracted the minimum number of components needed to secure the over-arching population level variation among the loci (`r pcadapt.params.LST[[MODE]]$min.variance.explained*10` % of the variation in loci). We then used Mahalanobis distances [@r398] to compute _P_ values and then q-values [using the \texttt{qvalue R} package; @r491]. Outlier loci were detected using a suitable false discovery rate ($q < `r pcadapt.params.LST[[MODE]]$alpha.level`$).

@@

The previous analysis resulted in an adaptive (if detected) and neutral genetic space for each species. For a given species, each planning unit occupied by the species was associated with a multi-dimensional point in the species' neutral genetic space. Planning units that were closer together in this space are occupied by individuals with similar polymorphisms in their neutral loci. Similarly, if the species was associated with adaptive loci, each planning unit occupied by the species was associated with a multi-dimensional point in the species' adaptive genetic space. By spreading out conservation effort across a given genetic space, and in turn securing planning units occupied by individuals with increasingly different polymorphisms, prioritizations can secure more genetic variation [see @r465 for discussion on attribute spaces].

>>>>

### Adaptive and neutral genetic data
To investigate the effectiveness of our supposed surrogates for adaptive and neutral genetic variation, we first needed to identify which of the sampled loci--if any--were adaptive. We used two outlier detection methods to achieve this [an individual- and a population-level method as recommended by @r495]. The basic premise underpinning such methods is that neutral loci are expected to exhibit a specific level of variation among populations, and loci that deviate from this expectation should be under selection [reviewed in @r480]. The advantage of these methods--in contrast with environmental association analyses [@r489]--is that they do not use environmental data to identify loci under selection, which would have biased our analysis. Loci identified as outliers in both analyses were treated as adaptive and the rest were treated as neutral. To avoid false-positives, we omitted loci from both outlier detection methods where the global frequency of the minor allele was $> 0.1$ and assumed they were neutral.

The first outlier detection method we used involved fitting multinominal-Dirichlet models implemented in \texttt{BayeScan} [version 2.1; @r456]. We adopted a similar methodology to Bothwell _et al._ [-@r455] and applied it to each of the species in the data set. Following their methodology, we first grouped conspecifics into genetic lineages to avoid falsely classifying loci as adaptive. To complete this first step, for each species, we fit the admixture and correlated alleles model implemented in \texttt{Structure} [version 2.3.4; XXXX] assuming various numbers of populations (K = `r min(structure.params.LST[[MODE]]$maxpops)`--`r max(structure.params.LST[[MODE]]$maxpops)`; `structure.params.LST[[MODE]]$numruns` replicates per K; `r structure.params.LST[[MODE]]$admburnin` admixture burnin iterations; `r structure.params.LST[[MODE]]$burnin` burnin iterations; `r structure.params.LST[[MODE]]$numreps` iterations used for inference). We used the variant of Evanno's K method used in \texttt{Structure Harvester} [XXX] to identify the most suitable number of populations separately for each species. We used \texttt{ClumPP} [version 1.1.2; @r459] to combine replicate runs to group individuals into populations (greedy algorithm using the _G_ static; `r structure.params.LST[[MODE]]$repeats` iterations). After the \texttt{ClumPP} analysis, if most of the individuals for a given species (> 50 %) had uncertain population memberships (< 75 % probability for most likely population) then we treated this species as containing only a single population. We then ran $\texttt{Bayescan}$ for each species using these populations [1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; @r456]. Additionally, we omitted individuals from the \texttt{Bayescan} analysis if their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate [$q \leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

The second outlier detection method involved fitting PCAs to identify outlier loci [using methods implemented in the \texttt{pcadapt R} package; version 3.0; @r487; @r496]. To enable comparisons between the two outlier detection analyses, we used the same individuals in this analysis as used in the \texttt{BayeScan} analysis. For each of the 27 species, we first imputed missing data to permit further analysis. Specifically, the missing value for a given locus for a given individual was replaced with the average frequency of that locus among all conspecifics. Next, we ran a PCA and extracted the minimum number of components needed to secure the over-arching population level variation among the loci (`r pcadapt.params.LST[[MODE]]$min.variance.explained*10` % of the variation in loci). We then used Mahalanobis distances [@r398] to compute _P_ values and then _q_-values [using the \texttt{qvalue R} package; @r491]. Outlier loci were detected using a suitable false discovery rate ($q < `r pcadapt.params.LST[[MODE]]$alpha.level`$).

@@

The previous set of analyses resulted in an adaptive (if detected) and neutral genetic space for each species. For a given species, each planning unit occupied by the species was associated with a multi-dimensional point in the species' neutral genetic space. Planning units that were closer together in this space are occupied by individuals with similar polymorphisms in their neutral loci. Similarly, if the species was associated with adaptive loci, each planning unit occupied by the species was associated with a multi-dimensional point in the species' adaptive genetic space. By spreading out conservation effort across a given genetic space, and in turn securing planning units occupied by individuals with increasingly different polymorphisms, prioritizations can secure more genetic variation [see @r465 for discussion on attribute spaces].
